Sequential algorithms to split and merge large 3D images

### 2017-05-29 paper.tex
Added comment on compression, following discussion with @ValHayot on Slack.

Lossless compression might reduce overall read and write times by
reducing seek time and data sizes. However, it needs to be implemented
on-the-fly, i.e., in chunks. See the work in~\cite{rajna2015speeding}
and \href{https://github.com/pauldmccarthy/indexed\_gzip}{corresponding
  implementation}.

>>>>

Lossless compression might reduce overall read and write times by
reducing seek time and data sizes. However, it needs to be implemented
on-the-fly, i.e., in chunks. See the work in~\cite{rajna2015speeding}
and
\href{https://github.com/pauldmccarthy/indexed\_gzip}{corresponding
  implementation}. This is straightforward to apply for random reads
but not for random writes. Multiple reads is the only merging strategy
that works with literally no seek in the reconstructed image which
could therefore potentially use in-memory compression.
